%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Modified Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.0 (07/04/2020)
% 
% Author
% Apur Misha(https://apurvmishra.xyz)
% Repository
% https://github.com/apurvmishra99/Modified-Deedy-Resume
% Original author of Deedy Resume:
% Debarghya Das (http://debarghyadas.com)
% His repository:
% https://github.com/deedydas/Deedy-Resume
%
%

%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage[utf8]{inputenc}
\usepackage{eurosym}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Will}{Struder}{ \urlstyle{same}\href{https://willstruder.com}{\bf willstruder.com} |
\href{mailto:willstruder@gmail.com}{\bf willstruder@gmail.com} | \bf (470)-708-1178 | \urlstyle{same}\href{https://github.com/willstrudel}{\bf Github} |
\urlstyle{same}\href{https://www.linkedin.com/in/will-struder}{\bf Linkedin}} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.66\textwidth} 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{Georgia Institute of Technology}
\descript{Full Stack Web Development Certificate}
\location{September \textbf{2021 } | Atlanta, Ga}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Healthtronics}
\descript{|\ Laser Technician }
\location{Nov \textbf{2019 } – June \textbf{2021} | Woodstock, Ga - Huntsville, Al}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Assisted physicians during surgery using holmium, greenlight, and co2 lasers.
\item Responsible for calculating energy levels and proper settings depending on the surgery, including fiber type/size.
\item Regularly transported lasers and fibers between hospitals while handling inventory of supplies needed for each case each week.
\end{tightemize}
\sectionsep

\runsubsection{United States Postal Service}
\descript{| Rural Carrier Assistant }
\location{Oct \textbf{2017 } – Nov \textbf{2019} | Woodstock, Ga}
\begin{tightemize}
\item Daily responsibilities included sorting, casing, delivering and receiving mail and/or packages to and from multiple dedicated routes throughout multiple cities.
\item During my time at the USPS, I had also trained new employees on how to sort, case, and deliver mail in a safe yet timely manner. 
\end{tightemize}
\sectionsep

\runsubsection{AT\&T}
\descript{| Installation Technician}
\location{Feb \textbf{2016 } - Sept \textbf{2017 } | Acworth, Ga}
\begin{tightemize}
\item As an Installation Technician, my time was primarily spent installing AT\&T Internet, TV, and Phone/VoIP services to residential and commercial properties.
\item Proficient with installation of copper, fiber, and satellite dish equipment, as well as troubleshooting repair tickets.
\end{tightemize}
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{enCapsulate}{ \urlstyle{same}\href{https://encapsulate.herokuapp.com/}{\bf encapsulate.herokuapp}}
\descript{| MongoDB, Express, React, Node}
\location{August \textbf{2021 }}
\begin{tightemize}
\item enCapsulate is the culmination of our bootcamp team, an e-commerce website deployed on Heroku. 
\item Researched shopping trends for minimalism and ethically friendly merchandise, bringing the public a new and innovative capsule wardrobe company.
\item Payment processing was done with the integration of the Stripe API.
\item Express used for server, MongoDB for the database, and Bcrypt for password encryption. 
\end{tightemize}
\sectionsep

\runsubsection{Little River Studio}{ \urlstyle{same}\href{https://littleriverstudio.org}{\bf littleriverstudio.org}}
\descript{| React, Tailwind CSS, EmailJS}
\location{Apr \textbf{2021 }}
\begin{tightemize}
\item Little River Studio is a small business offering numerous multimedia services.
\item Built with React and Tailwind CSS, the site was designed mobile first and mobile responsive.
\item Contact form using EmailJS, sends messages directly to personal Gmail account.
\item Deployed with GitHub Actions, hosted on custom Google Domain using GH Pages IP address. 
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{minipage}%
\hfill
\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{\textbf{Over 2000 lines:}}
HTML \textbullet{} Twailwind CSS \textbullet{} React JS \ \\ 
\location{\textbf{Over 1000 lines:}}
NodeJS \textbullet{} Javascript \\
\textbullet{} CSS \\
\location{\textbf{Familiar:}}
Express \textbullet{}
MongoDB \textbullet{ }MySQL 
\subsection{VCS \& Build Tools}
Git \textbullet{} CRA \textbullet{}Google Domains \textbullet{} Github/Github Actions
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
HTML/CSS/Git \\
Advanced CSS \\
Javascript \\
Web/3rd Party/Server-Side API's \\
NodeJS \\
OOP Programming \\
Express \\
SQL \\
React \\
MERN/State \\
 

\end{minipage}%
\end{document}  
\documentclass[]{article}
